Optimal (Multiway) Spatial Joins

### 2024-05-29 msj.tex
yufei

It remains to prove that no two distinct tuples $\bm{t}_1, \bm{t}_2 \in \J(R_1',...,R_{k-2}')$ can be mapped to the same tuple in $\J(R_1,..., R_{k-2},$ $H, V)$. Assume that this is not true, namely, both $\bm{t}_1$ and $\bm{t}_2$ are mapped to $(r_1, ..., r_{k-2}, h, v) \in \J(R_1,..., R_{k-2}, H, V)$. However, in this case, $\bm{t}_1[z]$ is the trimmed rectangle of $r_z$ for all $z \in [k-2]$, and $\bm{t}_2[z]$ is the trimmed rectangle of $r_z$ for all $z \in [k-2]$. This indicates $\bm{t}_1 = \bm{t}_2$, giving a contradiction.

>>>>

It remains to prove that no two distinct tuples $\bm{t}_1, \bm{t}_2 \in \J(R_1',...,$ $R_{k-2}')$ can be mapped to the same tuple in $\J(R_1,..., R_{k-2},$ $H, V)$. Assume that this is not true, namely, both $\bm{t}_1$ and $\bm{t}_2$ are mapped to $(r_1, ..., r_{k-2}, h, v) \in \J(R_1,..., R_{k-2}, H, V)$. However, in this case, $\bm{t}_1[z]$ is the trimmed rectangle of $r_z$ for all $z \in [k-2]$ and, at the same time, $\bm{t}_2[z]$ is the trimmed rectangle of $r_z$ for all $z \in [k-2]$. We thus have $\bm{t}_1 = \bm{t}_2$, giving a contradiction.
